---
title: "Chapter 2"
fig_caption: yes
output:
  pdf_document: 
    keep_tex: true


---
Loading the required libraries (R studio will warn you about non-installed libraries)


```{r load_libraries}
library(knitr)
library(qqplotr)
library(reshape2)
library(FrF2)
library(rsm)
```

To load the data-set

```{r load_data}
load(file =  "c:/temp/Emagma.RData")
```
 
Create the coded data

```{r create_coded_data_emagma}
doe <- data.frame(EMAGMA,CE,Screw.speed,is)
doe$x1 <- (doe$EMAGMA-mean(doe$EMAGMA))/5
doe$x2 <- (doe$CE-mean(doe$CE))/0.25
doe$x3 <- (doe$Screw.speed-mean(doe$Screw.speed))/50
doe11 <- doe[doe$EMAGMA!=15,]
doe22 <- doe11[doe11$CE!=0.25,]
```

Computing the scaled variance function for a 
design, based on a first order model

```{r scaled_variance_emagma_FO, fig.width=4, fig.height=4}
par(mfrow=c(1,1))
varfcn(doe, ~ FO(x1,x2,x3), contour = TRUE) 
```
Computing the scaled variance function for a design, based on a first order model with cross products

```{r scaled_variance_emagma_SO,  fig.width=4, fig.height=4}
par(mfrow=c(1,1))
varfcn(doe, ~ FO(x1,x2,x3)+TWI(x1,x2,x3), contour = TRUE)  
```

Computing the model and reporting the summary 
```{r rsm_model_EMAGMA,  fig.width=5, fig.height=5}
mod = rsm(is ~ FO(x1,x2,x3)+TWI(x1,x2,x3), data=doe)
summary(mod)
```

Diagnostic plot for the model

```{r rsm_model_EMAGMA_plot,  fig.width=4, fig.height=4}
par(mfrow=c(2,2))
plot(mod)
```

If you need a full factorial design you can rely 
on this syntax is for a full Factorial n=2 2 levels
```{r full_factorial2x2}
expand.grid(A = c("+", "-"), B = c("+", "-"))
```
of full Factorial n=3 with two levels
```{r full_factorial3x3}
expand.grid(A = c("+", "-"),
            B = c("+", "-"), C = c("+", "-"))
```
For fractional factorial you can use the command
```{r}
FrF2(nruns=8,nfactors=4)
```
And forPlackett-Burman
```{r}
pb(8)
```

For the Dataset OPT CABLES

```{r OPT_cables}

#setup lower (min = minus, "-") and higher(plus, "+") 
#and zero, for the factor
Amin = 0.025
Aplus = 0.050
Bmin = 170
Bplus  = 190
Azero  = 0.0375
Bzero = 180
stepB=10
stepA=0.0125

#response
p1 <- 1130
a <- 1078
b <- 1398
ab <- 1320
#
A0<- c(Amin,Aplus,Amin,Aplus)
B0 <- c(Bmin,Bmin,Bplus,Bplus)
y0 <- c(p1, a,b,ab)
block0 <- rep(1,length(A0))
doe0 <- data.frame(A0,B0,y0,block0)
colnames(doe0) <- c("A","B","y","block")

sumcoeff=4 #sum of the coefficients of the model 
rep=1 #number of replicate
Ahat <-  (a+ab)/2 - (p1+b)/2
Bhat <-  (b+ab)/2 - (p1+a)/2
ABhat <- (ab+p1)/2 -(a+b)/2
b1=Ahat/2
b2=Bhat/2
b12=ABhat/2
AC <- a+ab-p1-b
BC <- b+ab-p1-a
ABC <- ab+p1-a-b
#calculation of the sum of squares
SSA=(Ahat^2)/(sumcoeff*rep)
SSB=(Bhat^2)/(sumcoeff*rep)
SSAB=(ABhat)^2/(sumcoeff*rep)
```

Summary model 4 points dataset CABLE OPT
```{r model_opt_cables_4points }
coded.doe0 <- coded.data(doe0,
                         x1~(B-Bzero)/stepB,
                         x2~(A-Azero)/stepA)
mod0 = rsm(y ~(FO(x1,x2)+TWI(x1,x2)), data=coded.doe0)
summary(mod0)
```

Adding one central point

```{r model_opt_cables_5points}
p0=c(1205,1200,1195)
A1<- c(Amin,Aplus,Azero,Azero,Azero,Amin,Aplus)
B1 <- c(Bmin,Bmin,Bzero,Bzero,Bzero,Bplus,Bplus)
y1 <- c(p1, a, p0,b,ab)
block1 <- rep(1,length(A1))
doe1 <- data.frame(A1,B1,y1,block1)
colnames(doe1) <- c("A","B","y","block")
coded.doe1 <- coded.data(doe1, x1~(B-Bzero)/stepB, 
                         x2~(A-Azero)/stepA)
mod1 = rsm(y ~(FO(x1,x2)+TWI(x1,x2)), data=coded.doe1)
summary(mod1)

```


Diagnostic plots for model with central points for the dataset

```{r plot_cable_central, echo=FALSE, message=FALSE, warning=FALSE, fig.width=5, fig.height=5}
par(mfrow=c(2,2))
plot(mod1)
```

Plot of the interactions for model with central points

```{r plot_opt_cables_interactions, echo=FALSE, message=FALSE, warning=FALSE,  fig.width=4, fig.height=4}
par(mfrow=c(1,1))
contour(mod1, ~ x1 + x2, image = FALSE,
        at = summary(mod1)$canonical$xs,
        labcex=1.2, 
        xlabs=c("Mold T (°C)","Pulling Speed (m/s)"))
```

```{r  plot_opt_cables_interactions2, echo=FALSE, message=FALSE, warning=FALSE,  fig.width=5, fig.height=5}
par(mfrow=c(1,1))
persp(mod1, ~ x1 + x2,
      at = summary(mod1)$canonical$xs,
      contours = "black", zlab = "Tensile Strength (MPa)",
      xlabs = c("Mold Temp (°C)", "Speed (m/s)"),
      cex.lab = 1, ticktype="simple")
```

Second order for dataset with central point

```{r model_cable_seconorder}
mod1q = rsm(y ~(FO(x1,x2)+TWI(x1,x2)+SO(x1,x2)),
            data=coded.doe1)
summary(mod1q)

```

Dataset Faria with replicates

```{r model_cable_faria, load_data}
load(file =  "c:/temp/Faria2016.RData")
mod3 = rsm(y ~(FO(x1,x2)+TWI(x1,x2)+SO(x1,x2)),
           data=coded.doe3)
```


Plot of the interactions Faria

```{r plot_model_cable_faria, echo=FALSE, message=FALSE, warning=FALSE,  fig.width=5, fig.height=5}
par(mfrow=c(2,2))
plot(mod3)
```

```{r  plot_model_cable_faria_2,  echo=FALSE, message=FALSE, warning=FALSE,  fig.width=4, fig.height=4}

par(mfrow=c(1,1))
contour(mod3, ~ x1 + x2, 
        image = FALSE, at = summary(mod3)$canonical$xs,
        labcex=1.2, 
        xlabs=c("Mold T (°C)","Pulling Speed (m/s)"))

```
