---
title: "Chapter 1"
fig_caption: yes
output:
  pdf_document: 
    keep_tex: true


---

Loading the required libraries (R studio will warn you about non-installed libraries)

```{r load_libraries}
require(multcomp)
require(qqplotr)
require(knitr)
require(reshape2)

```

To load load the data-set (change your path according to the directory where you move the dataset)

```{r load_data}
load(file = "c:/temp/Epoxy.RData")
```
 
In order to see the structure of the data

```{r check_data}
str(all_data)
```

We can see that the data is a dataframe of four set A,B,C,D that represents the observation made by four laboratories on same variable
Due to kind of object we are using in R (dataframe) we get the info that we have 36 observations in 4 variables)
We calculate a statistical summary of our data 

```{r summary_for_the_data}
summary(all_data)
```

In order to calculate the variance

```{r variance}
var(all_data$A)
var(all_data$B)
var(all_data$C)
var(all_data$D)
```

For a stem and lef plot

```{r stem_and_leaf_plots}
stem(all_data$A, scale = 1)
stem(all_data$B, scale = 1)
stem(all_data$C, scale = 1)
stem(all_data$D, scale = 1)
```

Stripchart

```{r ex1_stripchart, fig.width=4, fig.height=2}
stripchart(all_data$A)
stripchart(all_data$B)
stripchart(all_data$C)
stripchart(all_data$D)
```

Histogram

```{r ex_1_histogram, fig.width=4, fig.height=4}
hist(all_data$A)
hist(all_data$B)
hist(all_data$C)
hist(all_data$D)
```

```{r ex1_box-whiskers, fig.width=4, fig.height=4}
boxplot(all_data)
```

In order to report a qqplot

```{r ex1_qq, fig.width=4, fig.height=4}
qqnorm(all_data$A, pch = 1, frame = FALSE)
qqline(all_data$A, col = "steelblue", lwd = 2)
qqnorm(all_data$B, pch = 1, frame = FALSE)
qqline(all_data$B, col = "steelblue", lwd = 2)
qqnorm(all_data$C, pch = 1, frame = FALSE)
qqline(all_data$C, col = "steelblue", lwd = 2)
qqnorm(all_data$D, pch = 1, frame = FALSE)
qqline(all_data$D, col = "steelblue", lwd = 2)
```

To calculate the z-scores

```{r}
za <- (all_data$A - mean(all_data$A)) / 
  sd(all_data$A)
zb <- (all_data$B - mean(all_data$B)) / 
  sd(all_data$B)
zc <- (all_data$C - mean(all_data$C)) /
  sd(all_data$C)
zd <- (all_data$D - mean(all_data$D)) /
  sd(all_data$D)

all_zscores <- data.frame(za,zb,zc,zd)

```

Example of a paired t-test

```{r}
library(broom)
library(purrr)
AB <- t.test(all_data$A, all_data$B)


```
Preparing the dataset for ANOVA

```{r}
all_melt<- data.frame(melt(all_data))

```

```{r}
lab.mod = aov(value ~ variable, data = all_melt)
summary(lab.mod)
```

Tukey Test

```{r}
tuk <- TukeyHSD(lab.mod)
tuk
```

In order to show another example of anova with different
models we load the other dataset

```{r}
load(file = "c:/temp/Hu_anova.RData")
hu_melt=data.melt
```

Considering the variables indipendend


```{r}
library(multcomp)
res.aov2 <- aov(value ~ label.a +
                  label.conc, data = hu_melt)
summary(res.aov2)

multg <- summary(glht(res.aov2, 
                      linfct = mcp(label.conc = "Tukey")))

```

Two way anova with interaction 

```{r ex1_anova_HU_res , fig.width=5, fig.height=5}
res.aov3 <- aov(value ~ label.a *label.conc,
                data =  hu_melt)
summary(res.aov3)


tuc.aov3 <- TukeyHSD(res.aov3)
tuc.aov3

par(mfrow=c(2,2))
plot(res.aov3)

aov_residuals <- residuals(object = res.aov3)

```


